
% \section{PhD thesis}
% \cvline{Title}{Detection and Tracking of Dynamic Objects. A MultiRobot Approach to Critical Infrastructures Surveillance.}
% \cvline{Supervisors}{Jaime del Cerro and Antonio Barrientos.}
% \cvline{Description}{My thesis was  focused in MultiRobot Systems for security and surveillance of Exterior Critical Infrastructures (CI). I have developed detection of dynamic objects algorithms for both aerial and ground robots. A Point Cloud based robot localization system has also been developed. Main skills and tools used in this thesis include but are not limited to: Mobile robotics, Simulation, Webots, ROS, PCL, OpenCV. \mbox{Download: \href{https://www.dropbox.com/s/tn7ooep4quv1nvl/PhD.GonzaloRCanosa.HR.4oct.pdf}{\textit{\textcolor{color1}{thesis.pdf}}}}}



\ifenglish
\newcommand{\GONCVsecPROJECTS}{Projects}
\fi
\ifgerman
\newcommand{\GONCVsecPROJECTS}{Projekte}
\fi
\ifspanish
\newcommand{\GONCVsecPROJECTS}{Proyectos}
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ifenglish
\newcommand{\GONCVsecPUBLICATIONS}{Publications}
\fi
\ifgerman
\newcommand{\GONCVsecPUBLICATIONS}{Publikationen}
\fi
\ifspanish
\newcommand{\GONCVsecPUBLICATIONS}{Publicaciones}
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ifenglish
\newcommand{\GONCVsecTESIS}{PhD thesis}
\fi
\ifgerman
\newcommand{\GONCVsecTESIS}{Doktorarbeit}
\fi
\ifspanish
\newcommand{\GONCVsecTESIS}{Tesis doctoral}
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ifenglish
\newcommand{\GONCVtesisINFO}{
\cvline{Title}{Detection and Tracking of Dynamic Objects. A MultiRobot Approach to Critical Infrastructures Surveillance.}
\cvline{Advisors}{Jaime del Cerro and Antonio Barrientos.}
}
\fi

\ifgerman
\newcommand{\GONCVtesisINFO}{
\cvline{Titel}{Detection and Tracking of Dynamic Objects. A MultiRobot Approach to Critical Infrastructures Surveillance.}
\cvline{Berater}{Jaime del Cerro and Antonio Barrientos.}
}
\fi

\ifspanish
\newcommand{\GONCVtesisINFO}{
\cvline{Título}{Detection and Tracking of Dynamic Objects. A MultiRobot Approach to Critical Infrastructures Surveillance.}
\cvline{Supervisores}{Jaime del Cerro and Antonio Barrientos.}
}
\fi

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ifenglish
\newcommand{\GONCVtesisDESCRIPTION}{
\cvline{Description}{My thesis was  focused in MultiRobot Systems for security and surveillance of Exterior Critical Infrastructures (CI). I have developed detection of dynamic objects algorithms for both aerial and ground robots. A Point Cloud based robot localization system has also been developed. Main skills and tools used in this thesis include but are not limited to: Mobile robotics, Simulation, Webots, ROS, PCL, OpenCV. \mbox{Download: \href{https://www.dropbox.com/s/tn7ooep4quv1nvl/PhD.GonzaloRCanosa.HR.4oct.pdf}{\textit{\textcolor{color1}{thesis.pdf}}}}}
}
\fi

\ifgerman
\newcommand{\GONCVtesisDESCRIPTION}{
\cvline{Description}{XXXXXXXXX \mbox{Download: \href{https://www.dropbox.com/s/tn7ooep4quv1nvl/PhD.GonzaloRCanosa.HR.4oct.pdf}{\textit{\textcolor{color1}{thesis.pdf}}}}}
}
\fi

\ifspanish
\newcommand{\GONCVtesisDESCRIPTION}{
\cvline{Descripción}{Mi tesis se centró en Sistemas Multirobot para la vigilancia y seguridad de Infraestructuras Críticas de Exteriores (ICE).  Desarrollé algoritmos de detección de objetos dinámicos tanto para robots terrestres como aéreos. Los algoritmos fueron implementados y probados tanto en sistemas simulados como en robots reales. También desarrollé un sistema de localización de robots basado en nubes de puntos. Las principales técnicas y herramientas utilizadas en la tesis fueron: Robots Móbiles, Simulaciones, Webots, ROS, PCL y OpenCV. \mbox{Download: \href{https://www.dropbox.com/s/tn7ooep4quv1nvl/PhD.GonzaloRCanosa.HR.4oct.pdf}{\textit{\textcolor{color1}{thesis.pdf}}}}}
}
\fi







  
